# Project 2024
<p>
Looking at the 2024 presidential election polling between President Biden and Trump in what would be a re-match of 2020.
</p>
 
## Polling with 3rd Parties
<p>
Third party candidates keep Biden and Trump below or just above 40's in their re-match according to these polls.
</p>
```{r,echo = FALSE, results = 'hide', warning = FALSE,message=FALSE, fig.height=5,fig.width=8,fig.align='center', fig.cap="How Third Parties candidates would affect the election"}  

library(ggplot2)
library(lubridate)
library(tidyverse) 
library(readxl)
ballots <- read_excel("~/ballots.xltx", sheet = "3_way")  
ballots$end_date<-mdy(ballots$end_date) 

ggplot(ballots, mapping = aes(x=end_date, y=Third_Party,color=answer))+
  geom_point(alpha=1/10,size=5) +
  geom_smooth(method = 'loess', formula = 'y~x',span=1, se=FALSE, lwd=2) +
  scale_colour_manual(values = c('blue','grey','orange',"green","red","yellow"))+
  labs(title = ' ',x='Date',caption = "sources:538.com(jamesstats.github.io)",
       y='%Percentage%', colour='Key')+
  theme_bw()+
  theme(legend.position = 'bottom')  
 
```

### Under 35 Age Group
<p>
Robert F.Kennedy Jr has strong support from the under 35 who seems to move away from both Biden and Trump and keep him in the low to high teens.
</P>
```{r,echo = FALSE, results = 'hide', warning = FALSE,message=FALSE, fig.height=5,fig.width=8,fig.align='center', fig.cap="How Third Parties candidates would affect the election"}  

library(ggplot2)
library(lubridate)
library(tidyverse) 
library(readxl)
ballots <- read_excel("~/ballots.xltx", sheet = "3_way")  
ballots$end_date<-mdy(ballots$end_date) 

ggplot(ballots, mapping = aes(x=end_date, y=Third_Party_U35,color=answer))+
  geom_point(alpha=1/10,size=5) +
  geom_smooth(method = 'loess', formula = 'y~x',span=1, se=FALSE, lwd=2) +
  scale_colour_manual(values = c('blue','grey','orange',"green","red","yellow"))+
  labs(title = 'Under 35 With Third Parties Candidates ',x='Date',
       caption = "sources:538.com(jamesstats.github.io)",
       y='%Percentage%', colour='Key')+
  theme_bw()+
  theme(legend.position = 'bottom')  
 
```

## Black voters
<p>
Biden is held in the 60's with black voters who he won with 90% of the vote in 2020 with Trump hoovering between 15% and 20% more than the 10% he received in 2020.
</p>
```{r,echo = FALSE, results = 'hide', warning = FALSE,message=FALSE, fig.height=5,fig.width=8,fig.align='center', fig.cap="How Third Parties candidates would affect the election"}  

library(ggplot2)
library(lubridate)
library(tidyverse) 
library(readxl)
ballots <- read_excel("~/ballots.xltx", sheet = "3_way")  
ballots$end_date<-mdy(ballots$end_date) 

ggplot(ballots, mapping = aes(x=end_date, y=Third_Party_BLK,color=answer))+
  geom_point(alpha=1/10,size=5) +
  geom_smooth(method = 'loess', formula = 'y~x',span=1, se=FALSE, lwd=2) +
  scale_colour_manual(values = c('blue','grey','orange',"green","red","yellow"))+
  labs(title = 'Black Voters With Third Parties Candidates ',x='Date',
       caption = "sources:538.com(jamesstats.github.io)",
       y='%Percentage%', colour='Key')+
  theme_bw()+
  theme(legend.position = 'bottom')  
 
```

## Hispanic voters
<p>
Robert F.Kennedy Jr seems to be taking hispanic voters from both Biden and Trump as he hoovers around 20%
while keeping them below 40%.
</p>
```{r,echo = FALSE, results = 'hide', warning = FALSE,message=FALSE, fig.height=5,fig.width=8,fig.align='center', fig.cap="How Third Parties candidates would affect the election"}  

library(ggplot2)
library(lubridate)
library(tidyverse) 
library(readxl)
ballots <- read_excel("~/ballots.xltx", sheet = "3_way")  
ballots$end_date<-mdy(ballots$end_date) 

ggplot(ballots, mapping = aes(x=end_date, y=Third_Party_HISP,color=answer))+
  geom_point(alpha=1/10,size=5) +
  geom_smooth(method = 'loess', formula = 'y~x',span=1, se=FALSE, lwd=2) +
  scale_colour_manual(values = c('blue','grey','orange',"green","red","yellow"))+
  labs(title = 'Hispanic Voters With Third Parties Candidates ',x='Date',
       caption = "sources:538.com(jamesstats.github.io)",
       y='%Percentage%', colour='Key')+
  theme_bw()+
  theme(legend.position = 'bottom')  
 
```

