--- 
title: "Projects Blog"
author: "by james"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
# Project Biden
<p>
Project Biden is tracking the approval ratings since the beginning of the first term in 2021. The polls used are sourced from *538.com* and filtered by their A ratings
<p/> 

## Biden approval tracking 
<p>
The tracking uses polls with rating of A by 538.com. The pollsters/firms used are ABC/Washington Post, Beacon/Shaw(Fox News),Cygnal(Republican),Marist Polls(NPR/PBS),Monmouth University, PPP(Democratic),Quinnipiac University,Selzer & Co(Grinnell College),Siena/NYT and suffolk University.
<p/>

```{r,echo = FALSE, results = 'hide', warning = FALSE,message=FALSE,fig.dpi=1080, fig.height=5,fig.width=9,fig.align='center'}  

library(ggplot2)
library(lubridate)
library(tidyverse) 
library(readxl)
buden_ <- read_excel("~/buden_.xltx", sheet = "clean") 
buden_$end_date<-mdy(buden_$end_date) 

ggplot(buden_, mapping = aes(x=end_date, y=share,color=approval))+
  geom_point(alpha=1/10,size=5) +
  geom_smooth(method = 'loess', formula = 'y~x',span=1, se=FALSE, lwd=2)+
  scale_colour_manual(values = c('red','grey','green'))+
  labs(title = 'Approve the job President Biden is doing?',caption = "sources:538.com(jamesstats.github.io/blog)",    x='Date',
       y='%Percentage%', colour='Key')+
  theme_bw()+
  theme(legend.position = 'bottom') 

```

## Methodology used by pollsters
<p>
Majority of the polls are conducted through the live phone and the others are a mix of live phone,online panel and text based. 
<p/> 

```{r,echo = FALSE, results = 'hide', warning = FALSE,message=FALSE,fig.dpi=1080,  fig.height=5,fig.width=8,fig.align='center'}  

library(ggplot2)
library(lubridate)
library(tidyverse) 
library(readxl)
buden_ <- read_excel("~/buden_.xltx", sheet = "clean") 
buden_$end_date<-mdy(buden_$end_date) 

ggplot(buden_, mapping = aes(x=end_date, y=share,color=approval))+
  geom_point(alpha=1/10,size=5) +
  geom_smooth(method = 'loess', formula = 'y~x',span=1, se=FALSE, lwd=2)+
  scale_colour_manual(values = c('red','grey','green'))+
  labs(title = 'How the polls are conducted',caption = "sources:538.com(jamesstats.github.io/blog)",       x='Date',
       y='%Percentage%', colour='Key')+
  theme_bw()+
  theme(legend.position = 'bottom') +
  facet_wrap(~methodology)  
```

## All the pollsters
<p>
All the pollsters compared against each other with the polls they have conducted and shows how Biden is viewed by the public.
<p/>

```{r,echo = FALSE, results = 'hide', warning = FALSE,message=FALSE,fig.dpi=1080, fig.height=5,fig.width=8,fig.align='center'}  

library(ggplot2)
library(lubridate)
library(tidyverse) 
library(readxl)
buden_ <- read_excel("~/buden_.xltx", sheet = "clean") 
buden_$end_date<-mdy(buden_$end_date) 

ggplot(buden_, mapping = aes(x=end_date, y=share,color=approval))+
  geom_point(alpha=1/10,size=5) +
  geom_smooth(method = 'loess', formula = 'y~x',span=1, se=FALSE, lwd=2)+
  scale_colour_manual(values = c('red','grey','green'))+
  labs(title = 'Pollsters and their polls',x='Date',caption = "sources:538.com(jamesstats.github.io/blog",
       y='%Percentage%', colour='Key')+
  theme_bw()+
  theme(legend.position = 'bottom') +
  facet_wrap(~pollster)  
``` 